### 2008-11-27 doc/sec/ManualofSecurityFramework.tex
Description about saml sp service in manual

>>>>

\subsubsection{SP Service and SAML2SSO Service Provider Handler}
{\selectlanguage{english}\color{black}
Service Provider servicer (SP service) implements the functionality of
Service Provider in SAML2 Web SSO profile. }

{\selectlanguage{english}\color{black}
Normally SP service will not be deployed independently, instead, it
should be deployed together with other services. The SLCS service is
the typical deployment about SP service. On the client side, client
developer should use the ClientSAML2Interface instead of
ClientInterface to call the client functionality. The SLCS client
(arcslcs) is the typical usage of \ ClientSAML2Interface.}

{\selectlanguage{english}\color{black}
Once the SP Service has cooperated with user agent and Identity Provider
(external) and succeeded to accomplish the SAML2 SSO profile, \ the SP
service will get the saml authentication assertion which asserts that
the authentication has succeeded, and then SP service will store this
assertion into session context.}

{\selectlanguage{english}\color{black}
SAML2 service provider handler (saml2ssoserviceprovider.handler) is the
security handler which will understand the authentication assertion and
make authorization decision according to this assertion.}

{\selectlanguage{english}\color{black}
The example configuration about using SP service and SAML2SSO service
provider handler can be seen in the configuration of SLCS service. }

{\selectlanguage{english}\color{black}
SP service is not only supposed to work together with SLCS service. But
if it is used to work together with other services, the client should
be developed on \ ClientSAML2Interface instead of ClientInterface.}

\subsubsection{SLCS service and client}
{\selectlanguage{english}\color{black}
Short-lived credential service (SLCS) is for signing short-lived x509
credential for user based user{\textquotesingle}s username/password
credential. Then the user can use the short-lived x509 credential to
access grid services/resources where x509 credential is required by
default. \ SLCS service should depend on the SP (Service provider)
service which is one of the participants of SAML2 SSO profile (SAML2
SSO profile is used for authenticating based on username/password
credential and getting SAML authentication assertion; and SAML
authentication assertion is then used as basis for signing short-lived
x509 credential).}

{\selectlanguage{english}\color{black}
a. \textbf{SLCS Service} }

{\selectlanguage{english}\color{black}
On the SLCS service side, a typical configuration should be like the
following.}

{\selectlanguage{english}\ttfamily\color{black}
{\textless}?xml version={\textquotedbl}1.0{\textquotedbl}?{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
{\textless}ArcConfig }

{\selectlanguage{english}\ttfamily\color{black}
\ \ xmlns={\textquotedbl}http://www.nordugrid.org/schemas/ArcConfig/2007{\textquotedbl}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ xmlns:tcp={\textquotedbl}http://www.nordugrid.org/schemas/ArcMCCTCP/2007{\textquotedbl}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ xmlns:tls={\textquotedbl}http://www.nordugrid.org/schemas/ArcMCCTLS/2007{\textquotedbl}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ xmlns:arcpdp={\textquotedbl}http://www.nordugrid.org/schemas/ArcPDP{\textquotedbl}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ xmlns:slcs={\textquotedbl}http://www.nordugrid.org/schemas/ArcConfig/2007/slcs{\textquotedbl}
}

{\selectlanguage{english}\ttfamily\color{black}
{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ {\textless}ModuleManager{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../hed/mcc/http/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../hed/mcc/tls/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../hed/mcc/soap/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../hed/mcc/tcp/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../hed/pdc/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../services/saml/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Path{\textgreater}../../services/slcs/.libs/{\textless}/Path{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}/ModuleManager{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}mcctcp{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}mcctls{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}mcchttp{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}mccsoap{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}arcpdc{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}saml2sp{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Plugins{\textgreater}{\textless}Name{\textgreater}slcs{\textless}/Name{\textgreater}{\textless}/Plugins{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}Chain{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}tcp.service{\textquotedbl}
id={\textquotedbl}tcp{\textquotedbl}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}tls{\textquotedbl}/{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tcp:Listen{\textgreater}{\textless}tcp:Port{\textgreater}60000{\textless}/tcp:Port{\textgreater}{\textless}/tcp:Listen{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}tls.service{\textquotedbl}
id={\textquotedbl}tls{\textquotedbl}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}http{\textquotedbl}/{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:KeyPath{\textgreater}./testkey-nopass.pem{\textless}/tls:KeyPath{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:CertificatePath{\textgreater}./testcert.pem{\textless}/tls:CertificatePath{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}!-{}-tls:CACertificatePath{\textgreater}./cacert.pem{\textless}/tls:CACertificatePath-{}-{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:ClientAuthn{\textgreater}false{\textless}/tls:ClientAuthn{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}http.service{\textquotedbl}
id={\textquotedbl}http{\textquotedbl}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}plexer{\textquotedbl}{\textgreater}POST{\textless}/next{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}/Component{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Plexer
name={\textquotedbl}plexer.service{\textquotedbl}
id={\textquotedbl}plexer{\textquotedbl}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}samlsp{\textquotedbl}{\textgreater}/saml2sp{\textless}/next{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}soap{\textquotedbl}{\textgreater}/slcs{\textless}/next{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}/Plexer{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Component
name={\textquotedbl}soap.service{\textquotedbl}
id={\textquotedbl}soap{\textquotedbl}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}slcs{\textquotedbl}/{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}SecHandler
name={\textquotedbl}\textcolor[rgb]{0.8627451,0.13725491,0.0}{saml2ssoserviceprovider.handler}{\textquotedbl}
id={\textquotedbl}saml2ssosp{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}/{\textgreater}}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ {\textless}/Component{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Service
name={\textquotesingle}\textcolor[rgb]{0.77254903,0.0,0.043137256}{saml.sp}{\textquotesingle}
id={\textquotesingle}samlsp{\textquotesingle}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}MetaDataLocation{\textgreater}./test\_metadata.xml{\textless}/MetaDataLocation{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}ServiceProviderName{\textgreater}https://squark.uio.no/shibboleth-sp{\textless}/ServiceProviderName{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}/Service{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}Service
name={\textquotedbl}\textcolor[rgb]{0.8627451,0.13725491,0.0}{slcs.service}{\textquotedbl}
id={\textquotedbl}slcs{\textquotedbl}{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}next
id={\textquotedbl}slcs{\textquotedbl}/{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}slcs:CACertificate{\textgreater}./CAcert.pem{\textless}/slcs:CACertificate{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}slcs:CAKey{\textgreater}./CAkey.pem{\textless}/slcs:CAKey{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}slcs:CASerial{\textgreater}./CAserial{\textless}/slcs:CASerial{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ \ \ \ \ {\textless}/Service{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}/Chain{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
{\textless}/ArcConfig{\textgreater} }

{\selectlanguage{english}\color{black}
SLCS service and SP service should together be configured by using the
Plexer. SP service is directly based on http and SLCS is directly based
on soap. }

{\selectlanguage{english}\color{black}
SLCS service should specifically include the CA credential (certificate
and key file) and the serial number file (which includes the serial
number of each signed certificate).}

{\selectlanguage{english}\color{black}
\textbf{Note}: When deploying the SLCS service, service administrator
should deploy a dedicated IdP (Identity Provider) which can be assigned
as authentication/attribute authority, or the users should have already
had his own IdP. And the IdP information (authentication URL and
attribute authority URL) should have already been included into the
metadata of above configuration (e.g. test\_metadata.xml). On the other
hand, the SP (SP service) information (assertion consuming URL) should
also have been included into the metadata of the IdP.}

{\selectlanguage{english}\color{black}
After the whole process, user only needs to authentication with his
existing IdP and can get back the x509 credential.}

{\selectlanguage{english}\color{black}
Shibboleth IdP (http://shibboleth.internet2.edu) is used for the current
solution of IdP, since it is widely deployed for other AAI
(Authentication and Authority Infrastructure). There is a test IdP
deployed in
\href{https://squark.uio.no:8443/}{https://squark.uio.no:8443}
(idpname: https://squark.uio.no/idp/shibboleth), you can use the SP
from \url{https://sp.testshib.org/} to test the validity of the test
IdP. And also you can installed your own IdP which is supposed to
authenticates the users from your own organization.}

{\selectlanguage{english}\color{black}
b. \textbf{SLCS client}}

{\selectlanguage{english}\color{black}
On the SLCS client side, there is a client utility called
{\textquotedblleft}arcslcs{\textquotedblright}. \ The command option
for arcslcs is as following:}

{\selectlanguage{english}\color{black}
Application Options: }

{\selectlanguage{english}\color{black}
\ \ {}-S, -{}-url=url \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ URL of SLCS service
}

{\selectlanguage{english}\color{black}
\ \ {}-I, -{}-idp=string \ \ \ \ \ \ \ \ \ \ \ \ IdP name }

{\selectlanguage{english}\color{black}
\ \ {}-U, -{}-user=string \ \ \ \ \ \ \ \ \ \ \ User account to IdP }

{\selectlanguage{english}\color{black}
\ \ {}-P, -{}-password=string \ \ \ \ \ \ \ Password for user account to
IdP }

{\selectlanguage{english}\color{black}
\ \ {}-Z, -{}-keysize=number \ \ \ \ \ \ \ \ Key size of the private key
(512, 1024, 2048) }

{\selectlanguage{english}\color{black}
\ \ {}-K, -{}-keypass=passphrase \ \ \ \ Private key passphrase }

{\selectlanguage{english}\color{black}
\ \ {}-L, -{}-lifetime=period \ \ \ \ \ \ \ Lifetime of the certificate,
start with current time, hour as unit }

{\selectlanguage{english}\color{black}
\ \ {}-D, -{}-storedir=directory \ \ \ \ Store directory for key and
signed certificate }

{\selectlanguage{english}\color{black}
\ \ {}-c, -{}-conffile=filename \ \ \ \ \ configuration file (default
\~{}/.arc/client.xml) }

{\selectlanguage{english}\color{black}
An example is:}

{\selectlanguage{english}\color{black}
./arcslcs -S https://127.0.0.1:60000/slcs -I
https://squark.uio.no/idp/shibboleth -U root -P aa1122 -D
/home/wzqiang/arc-0.9/src/clients/credentials -c client.xml }

{\selectlanguage{english}\color{black}
Note user should input the {\textquotedblleft}IdP
name{\textquotedblright} is the corresponding Identity Provider (one of
the participants of SAML2 SSO profile) name to which the user would
authentication against by using its username/password credential. And
the name is stored inside the metadata on both SP service and IdP
provider, and it is used by SP service to get the authentication URL
for username/password based authentication.}

{\selectlanguage{english}\color{black}
And the {\textquotedblleft}user{\textquotedblright} and
{\textquotedblleft}password{\textquotedblright} is the credential which
will be used to authentication against IdP.}

{\selectlanguage{english}\color{black}
The {\textquotedblleft}conffile{\textquotedblright} can be another
option for all of the above options, see the following as an example:}

{\selectlanguage{english}\ttfamily\color{black}
{\textless}ArcConfig{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}!-{}- change the paths below to the location of your user
certs -{}-{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}!-{}- here only trusted certificates are set. Because this
arcslcs is }

{\selectlanguage{english}\ttfamily\color{black}
\ not supposed to have x509 credential before the samlsso profile has
been }

{\selectlanguage{english}\ttfamily\color{black}
\ (by using client{\textquotesingle}s username/password credential)
passed and the SLCS }

{\selectlanguage{english}\ttfamily\color{black}
\ service succeeded to repond this client with the signed x509
credential. }

{\selectlanguage{english}\ttfamily\color{black}
\ On the SLCS service{\textquotesingle}s configuration: ClientAuthn
should be off.-{}-{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}!-{}-KeyPath{\textgreater}./testkey-nopass.pem{\textless}/KeyPath-{}-{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}!-{}-CertificatePath{\textgreater}./testcert.pem{\textless}/CertificatePath-{}-{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}CACertificatesDir{\textgreater}./certificates{\textless}/CACertificatesDir{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}SLCSURL{\textgreater}https://127.0.0.1:60000/slcs{\textless}/SLCSURL{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}IdPname{\textgreater}https://squark.uio.no/idp/shibboleth{\textless}/IdPname{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}Username{\textgreater}root{\textless}/Username{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}Password{\textgreater}aa1122{\textless}/Password{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}Keysize{\textgreater}1024{\textless}/Keysize{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}Keypass{\textgreater}123456{\textless}/Keypass{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}CertLifetime{\textgreater}24{\textless}/CertLifetime{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}StoreDir{\textgreater}./{\textless}/StoreDir{\textgreater}
}

{\selectlanguage{english}\ttfamily\color{black}
\ {\textless}Debug{\textgreater}INFO{\textless}/Debug{\textgreater} }

{\selectlanguage{english}\ttfamily\color{black}
{\textless}/ArcConfig{\textgreater} }
